---
title: "Analysis of Terapixel Visualization"
author: "Siddharthan Saravanan"
date: "25/01/2021"
output: pdf_document
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

# Introduction

Terapixel images offer an intuitive, accessible way to present information sets to stakeholders, allowing viewers to interactively browse big data across multiple scales.The challenge that was addressed is how to deliver the SuperComputer scale resources which are needed to compute a realistic Terapixel image and the data was captured by the Newcastle Urban Observatory. The Terapixel image obtained from the data can be viewed through this link, http://terapixel.wasabi.1024.s3.eu-central-1.wasabisys.com/vtour/index.html.



```{r cars}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
