---
title: "Analysis of Terapixel Visualization"
author: "Siddharthan Saravanan"
date: "25/01/2021"
output: pdf_document
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

# Introduction

Terapixel images offer an intuitive, accessible way to present information sets to stakeholders, allowing viewers to interactively browse big data across multiple scales.The challenge that was addressed is how to deliver the SuperComputer scale resources which are needed to compute a realistic Terapixel image and the data was captured by the Newcastle Urban Observatory. The Terapixel image obtained from the data can be viewed through this link, http://terapixel.wasabi.1024.s3.eu-central-1.wasabisys.com/vtour/index.html.

This scalable architecture was created for cloud based visualization where it is possible to deploy and pay for only as needed. The Terapixel image is created in such a way that, it can be viewed in all sorts of devices irrespective of its computational power. This analysis report is to find out the outliers using different GPU's which can be analysed for the improvement of the performance of the Super Computer in generating the image.

## Insights of Data

The dataset which is taken for the analysis was created from application checkpoint and system metric output from the production of the Terapixel image. It particularly consists of three datasets which are application-Checkpoints, GPU and Task-x-y. 

```{r cars}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
